BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-15 Msc-Slides/main.tex
Small fix to slides

A dynamic binary analysis
technique in which the behaviour of an application is inspected at run-time via the
injection of analysis code. 
\bigskip
\begin{block}{}
\begin{lstlisting}[basicstyle=\ttfamily\large,xleftmargin=50pt]
<@\textcolor{red}{record(arg1)}@> 
retval = libcall(arg1, &arg2)
<@\textcolor{red}{record(retval, *arg2)}@> 
\end{lstlisting}
\end{block}
\bigskip
\bigskip
\textbf{Problem 1}: existing products have limited logging capabilites

@@

\subsection{Al-Khaser}
\begin{frame}
    \frametitle{Evaluation with Al-Khaser}
	\textbf{Al-Khaser} is an open-source application which performs common checks employed by malware families to determine if they are being
executed in an analysis environment
\\\medskip
Checks divided in categories:
\begin{itemize}
\item \textbf{Anti-Debugging}
\item \textbf{Timing-based}
\item \textbf{Human Interaction Detection}
\item \textbf{Anti-Virtualization}
\item \textbf{Anti-Analysis}
\end{itemize}
\bigskip
\begin{beamerboxesrounded}[shadow=true]{}
BlueTracer was undetected with respect to all the checks!
\end{beamerboxesrounded}

@@

File system artifacts can be checked in order to uncover the presence of a virtualized environment
\vspace*{0.5cm}

>>>>

A dynamic binary analysis
technique in which the behaviour of an application is inspected at run-time via the
injection of analysis code. 
\bigskip
\begin{block}{}
\begin{lstlisting}[basicstyle=\ttfamily\large,xleftmargin=50pt]
<@\textcolor{red}{record(libcall, arg1)}@> 
retval = libcall(arg1, &arg2)
<@\textcolor{red}{record(retval, *arg2)}@> 
\end{lstlisting}
\end{block}
\bigskip
\bigskip
\textbf{Problem 1}: existing products have limited logging capabilites

@@

\subsection{Al-Khaser}
\begin{frame}
    \frametitle{Evaluation with Al-Khaser}
	\textbf{Al-Khaser} is an open-source application which performs common checks employed by malware families to determine if they are being
executed in an analysis environment.
\\\medskip
Checks divided in categories:
\begin{itemize}
\item \textbf{Anti-Debugging}
\item \textbf{Timing-based}
\item \textbf{Human Interaction Detection}
\item \textbf{Anti-Virtualization}
\item \textbf{Anti-Analysis}
\end{itemize}
\bigskip
\begin{beamerboxesrounded}[shadow=true]{}
BlueTracer was undetected with respect to all the checks!
\end{beamerboxesrounded}

@@

File system artifacts can be checked in order to uncover the presence of a virtualized environment.
\vspace*{0.5cm}
